Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-04-26 paper/main.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[maxcitenames=1,style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfig}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{textgreek}
\usepackage{caption}
%\usepackage{subcaption}

@@

There are also sources showing that binding energy calculations may be poor predictors of RBS strength \cite{Saito2020,Sherer1980}.\\

@@

\begin{figure}[t]
\centering
\subfloat{\label{main:c}\includegraphics[scale=.4]{plots/Hd_Heatmap.png}}\par\medskip
\begin{minipage}{.5\linewidth}
\centering
\subfloat[]{\label{main:a}\includegraphics[scale=.4]{plots/Hd_Heatmap.png}}
\end{minipage}
\begin{minipage}{.5\linewidth}
\centering
\subfloat[]{\label{main:b}\includegraphics[scale=.4]{plots/Hd_Heatmap.png}}
\end{minipage}
\begin{minipage}{.5\linewidth}
\centering
\subfloat[]{\label{main:b}\includegraphics[scale=.4]{plots/Hd_Heatmap.png}}
\end{minipage}
\caption{Characteristics of the sequences.}
\label{fig:characteristics}
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[maxcitenames=1,style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{textgreek}
\usepackage{caption}
\usepackage{subcaption}
% \usepackage{subfigure}

@@

There are also sources showing that binding energy calculations may be poor predictors of RBS strength \cite{Saito2020,Sherer1980} . This is reinforced by studies suggesting that RNA secondary structure is potentially a more important feature in TIR determination \cite{DESMIT1994,EspahBorujeni2016} .\\

@@

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=1.2]{plots/logo.pdf}
         \caption{$y=x$}
         \label{fig:y equals x}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.5]{plots/Patterns.png}
         \caption{$y=3sinx$}
         \label{fig:three sin x}
     \end{subfigure}
     \vskip\baselineskip
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.5]{plots/Hd_Heatmap.png}
         \caption{$y=5/x$}
         \label{fig:five over x}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.5]{plots/Histogram.png}
         \caption{$y=5/x$}
         \label{fig:five over x}
     \end{subfigure}
        \caption{Three simple graphs}
        \label{fig:three graphs}
\end{figure}
